Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
work p1

>>>>

<!-- intro -->
Complex animal social systems are influenced by biological and observation scales.
By parsing social systems into contexts using multilayer networks,
we observed differences across social, spatial and temporal scales.
Social scale
Spatial and temporal contexts 
including habitats, discrete patches and fragmented landscapes, as well as across 
seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
Sociality exists across scales characterized by different 
types of behaviours as well as spatial and temporal thresholds defining these. 
Our results highlight the influence of social, spatial and temporal scales
on multilayer animal social networks, showing a requirement to consider biologically
relevant scales when selecting observational scales for a given study. 
<!-- intro -->
